Scalable Clustering of Genotype Information using MapReduce

### 2014-05-01 doc/publications/incob2014/paper.tex
Added a couple of tables templates

%% Use of \listoftables is discouraged.
%%
\section*{Tables}
\begin{table}[h!]
\caption{Datasets used in this study.}
      \begin{tabular}{lcc}
        \hline
           & individuals  & variants  \\ \hline
        Chr1 subset & & \\
        1000genomes trios & & \\
        hapmap & ... & ..  \\ \hline
      \end{tabular}
      \label{datasets}
\end{table}

>>>>

%% Use of \listoftables is discouraged.
%%
\section*{Tables}
\begin{table}[h!]
\caption{Datasets used in this study.}
      \begin{tabular}{lcc}
        \hline
           & individuals  & variants  \\ \hline
        Chr1 subset & 1024 & 3,007,196 \\
        1000genomes trios & 1024 & ...\\
        hapmap & ... & ...  \\ \hline
      \end{tabular}
      \label{datasets}
\end{table}

\begin{table}[h!]
\caption{Adjusted Rand index (accuracy).}
      \begin{tabular}{lccc}
        \hline
           & Chr1 subset & 1000genomes trios  & hapmap \\ \hline
        Mahout, k=4 & 0.664 & ..&..\\
        Mahout, k=10 & 0.714 & ..&..\\
        Mahout, k=20 & 0.769 & .. & ..\\ 
        Mahout, k=30 & 0.728 & .. & ..\\ 
        R, k=4 & .. & - & -\\
        R, k=10 & .. & - & -\\
        R, k=20 & .. & - & -\\ 
        R, k=30 & .. & - & -\\ \hline
      \end{tabular}
      \label{datasets}
\end{table}

\begin{table}[h!]
\caption{Time taken to cluster samples (k=20).}
      \begin{tabular}{lccc}
        \hline
           & Chr1 subset & 1000genomes trios  & hapmap \\ \hline
        Mahout, 1 node & .. & ..&..\\
        Mahout, 2 nodes & .. & ..&..\\
        Mahout, 3 nodes & .. & .. & ..\\ 
        Mahout, 4 nodes & .. & .. & ..\\ 
        R & .. & - & -\\ \hline
      \end{tabular}
      \label{datasets}
\end{table}
